Modeling the Impact of Commodity Prices and Interest Rates on the CAD/USD Exchange Rate: An Analysis of Key Drivers Using Bank Rate and BCPI

### 2024-12-03 paper/paper.qmd
update (@) to [@]

- **data cleaning** The tidyverse package was used for efficient data manipulation and visualization (@tidyverse), lubridate was employed for handling date-time operations (@lubridate), and arrow facilitated reading and writing large data sets in parquet format (@arrow).

>>>>

- **data cleaning** The tidyverse package was used for efficient data manipulation and visualization [@tidyverse], lubridate was employed for handling date-time operations [@lubridate], and arrow facilitated reading and writing large data sets in parquet format [@arrow].
